Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2013-03-22 documents/mixtures/mixture_models.tex
Ciotti & Bertin ref fix
Add paragraph about gammaincinv, and call out Bosch in acks

@@

\acknowledgements It is a pleasure to thank
      Brendon Brewer (Auckland),
      Jim Bosch (Princeton),
      Kevin Bundy (IPMU),
      Luca Ciotti (Bologna),
      Rachel Mandelbaum (CMU),
      Chien Peng (OCIW),
      and an anonymous referee
for valuable comments.  This work was supported in part by NASA (grant
NNX12AI50G) and the NSF (grant IIS-1124794).  All the results shown in
the figures and tables and more are available in machine-readable form
from author DWH upon request.

\begin{thebibliography}{70}
\bibitem[Bendinelli(1991)]{bendinelli}
Bendinelli,~O., 1991, \apj, 366, 599
\bibitem[Bendinelli et al.(1993)]{bendi}
Bendinelli,~O., Ciotti,~L., \& Parmeggiani,~G.\ 1993, \aap, 279, 668 
\bibitem[Bendinelli \& Parmeggiani(1995)]{bendinelli2}
Bendinelli,~O. \& Parmeggiani,~G., 1995, \aj, 109, 572
\bibitem[Bosch(2010)]{bosch}
Bosch,~J., 2010, \aj, 140, 870
\bibitem[Bovy \etal(2011a)]{xd}
Bovy,~J., Hogg,~D.~W., \& Roweis,~S., 2011, Ann. Appl. Stat., 5, 1657
\bibitem[Bovy \etal(2011b)]{xdqso}
Bovy,~J., \etal, 2011, \apj, 729, 141
\bibitem[Bovy \etal(2012)]{xdqsoz}
Bovy,~J. \etal, 2012, \aj, 749, 41
\bibitem[Bundy \etal(2012)]{bundy}
Bundy,~K. \etal, \aj, in press
\bibitem[Cappellari(2002)]{cappellari}
Cappellari,~M., 2002, \mnras, 333, 400
\bibitem[Ciotti \& Bertin(1999)]{ciotti}
Ciotti,~L. \& Bertin,~G., 1999, \aa, 352, 447
\bibitem[de~Vaucouleurs(1948)]{dev}
de~Vaucouleurs,~G., 1948, Annales d'Astrophysique, 11, 247
\bibitem[Emsellem \etal(1994)]{emsellem}
Emsellem,~E., Monnet,~G., Bacon,~R., \& Nieto,~J.-L., 1994, \aap, 285, 739
\bibitem[Kochanek et al.(2000)]{kochanek}
Kochanek,~C.~S., Falco,~E.~E., Impey,~C.~D., et al., 2000, \apj, 535, 692
\bibitem[Lupton \etal(2001)]{lupton}
Lupton,~R., Gunn,~J.~E., Ivezic,~Z., Knapp,~G.~R., Kent,~S.~M., \& Yasuda,~N., 2001, ASPC, 238, 269
\bibitem[Peng \etal(2002)]{galfit}
Peng,~C.~Y., Ho, L.~C., Impey,~C.~D., \& Rix,~H.-W., 2002, \aj, 124, 266
\bibitem[S{\'e}rsic(1963)]{ser}
S{\'e}rsic,~J.~L., 1963, Boletin de la Asociacion Argentina de Astronomia La Plata Argentina, 6, 41
\bibitem[Shaw(2012)]{shaw}
Shaw,~R.~A., ed., 2012, LSST Data Challenge Handbook (Version 2.0; Tucson, AZ: LSST Corp.)
\bibitem[Simard et al.(2011)]{bulgedisk}
Simard,~L., Mendel,~J.~T., Patton,~D.~R., Ellison,~S.~L., \& McConnachie,~A.~W., 2011, \apjs, 196, 11
\bibitem[Spergel(2010)]{spergel}
Spergel,~D.~N.\ 2010, \apjs, 191, 58
\bibitem[Trujillo \etal(2001)]{trujillo}
Trujillo,~I., Aguerri,~J.~A.~L., Cepa,~J., \& Guti{\'e}rrez,~C.~M., 2001, \mnras, 321, 269 
\bibitem[van~den~Bosch et al.(2008)]{vdb}
van~den~Bosch,~R.~C.~E., van de Ven,~G., Verolme,~E.~K., Cappellari,~M., \& de~Zeeuw,~P.~T., 2008, \mnras, 385, 647
\end{thebibliography}

>>>>

\cite{ciotti} give an equation for $\alpha^{\ser(n)}$ in their
equation 5:
\begin{eqnarray}
\gamma(2 n, \alpha^{\ser(n)}) &=& \frac{\Gamma(2 n)}{2}
\end{eqnarray}
where $\gamma$ is the \emph{left} or \emph{lower} incomplete gamma function,
\begin{eqnarray}
\gamma(a, x) &=& \int_0^x \exp(-t) \, t^{a-1} \, \mathrm{d} t \quad .
\end{eqnarray}
Fortunately for us, this can be evaluated using
\begin{eqnarray}
\alpha^{\ser(n)} &=& \mathrm{gammaincinv}(2 n, \, \frac{1}{2})
\end{eqnarray}
using the gammaincinv (inverse incomplete gamma) function in the
\project{scipy.special} library.

@@

\acknowledgements It is a pleasure to thank
      Brendon Brewer (Auckland),
      Kevin Bundy (IPMU),
      Luca Ciotti (Bologna),
      Rachel Mandelbaum (CMU),
      Chien Peng (OCIW),
      and an anonymous referee
for valuable comments.
%
We thank Jim Bosch (Princeton) for bringing to our attention the
\emph{gammaincinv} function.
%
  This work was supported in part by NASA (grant
NNX12AI50G) and the NSF (grant IIS-1124794).  All the results shown in
the figures and tables and more are available in machine-readable form
from author DWH upon request.

\begin{thebibliography}{70}
\bibitem[Bendinelli(1991)]{bendinelli}
Bendinelli,~O., 1991, \apj, 366, 599
\bibitem[Bendinelli et al.(1993)]{bendi}
Bendinelli,~O., Ciotti,~L., \& Parmeggiani,~G.\ 1993, \aap, 279, 668 
\bibitem[Bendinelli \& Parmeggiani(1995)]{bendinelli2}
Bendinelli,~O. \& Parmeggiani,~G., 1995, \aj, 109, 572
\bibitem[Bosch(2010)]{bosch}
Bosch,~J., 2010, \aj, 140, 870
\bibitem[Bovy \etal(2011a)]{xd}
Bovy,~J., Hogg,~D.~W., \& Roweis,~S., 2011, Ann. Appl. Stat., 5, 1657
\bibitem[Bovy \etal(2011b)]{xdqso}
Bovy,~J., \etal, 2011, \apj, 729, 141
\bibitem[Bovy \etal(2012)]{xdqsoz}
Bovy,~J. \etal, 2012, \aj, 749, 41
\bibitem[Bundy \etal(2012)]{bundy}
Bundy,~K. \etal, \aj, in press
\bibitem[Cappellari(2002)]{cappellari}
Cappellari,~M., 2002, \mnras, 333, 400
\bibitem[Ciotti \& Bertin(1999)]{ciotti}
Ciotti,~L. \& Bertin,~G., 1999, \aap, 352, 447
\bibitem[de~Vaucouleurs(1948)]{dev}
de~Vaucouleurs,~G., 1948, Annales d'Astrophysique, 11, 247
\bibitem[Emsellem \etal(1994)]{emsellem}
Emsellem,~E., Monnet,~G., Bacon,~R., \& Nieto,~J.-L., 1994, \aap, 285, 739
\bibitem[Kochanek et al.(2000)]{kochanek}
Kochanek,~C.~S., Falco,~E.~E., Impey,~C.~D., et al., 2000, \apj, 535, 692
\bibitem[Lupton \etal(2001)]{lupton}
Lupton,~R., Gunn,~J.~E., Ivezic,~Z., Knapp,~G.~R., Kent,~S.~M., \& Yasuda,~N., 2001, ASPC, 238, 269
\bibitem[Peng \etal(2002)]{galfit}
Peng,~C.~Y., Ho, L.~C., Impey,~C.~D., \& Rix,~H.-W., 2002, \aj, 124, 266
\bibitem[S{\'e}rsic(1963)]{ser}
S{\'e}rsic,~J.~L., 1963, Boletin de la Asociacion Argentina de Astronomia La Plata Argentina, 6, 41
\bibitem[Shaw(2012)]{shaw}
Shaw,~R.~A., ed., 2012, LSST Data Challenge Handbook (Version 2.0; Tucson, AZ: LSST Corp.)
\bibitem[Simard et al.(2011)]{bulgedisk}
Simard,~L., Mendel,~J.~T., Patton,~D.~R., Ellison,~S.~L., \& McConnachie,~A.~W., 2011, \apjs, 196, 11
\bibitem[Spergel(2010)]{spergel}
Spergel,~D.~N.\ 2010, \apjs, 191, 58
\bibitem[Trujillo \etal(2001)]{trujillo}
Trujillo,~I., Aguerri,~J.~A.~L., Cepa,~J., \& Guti{\'e}rrez,~C.~M., 2001, \mnras, 321, 269 
\bibitem[van~den~Bosch et al.(2008)]{vdb}
van~den~Bosch,~R.~C.~E., van de Ven,~G., Verolme,~E.~K., Cappellari,~M., \& de~Zeeuw,~P.~T., 2008, \mnras, 385, 647
\end{thebibliography}
